A meta-analysis of powdery mildew yield loss mitigation strategies in Australian mungbean

### 2020-06-23 03_Prep_data.Rmd
small edits for more logical flow

Using the model without dose produces a lower AIC, however we should accept the data with dose as there is a significant difference between the models and we should accept the more complicated model `m2`.
We will try and evaluate dose in the meta-analysis, however for now we will remove the dose factor to reduce the possibility of overfitting the model.

```{r}
slimmer_PM_dat$trial <- slimmer_PM_dat$trial_noDose
slimmer_PM_dat <-
   slimmer_PM_dat[, colnames(slimmer_PM_dat) != "trial_noDose"] #remove second trial column
write.csv(slimmer_PM_dat, file = "cache/slimmer_PM_clusterdat.csv", row.names = FALSE)
```

@@

```{r}
slimmer_PM_dat <- read.csv(here("cache/slimmer_PM_clusterdat.csv"))

slimmer_PM_dat$D_pres <- NA_character_

>>>>

Using the model without dose produces a lower AIC, however we should accept the data with dose as there is a significant difference between the models and we should accept the more complicated model `m2`.
We will retain dose as a variable inside the `trial` factor.

```{r saveDat}
slimmer_PM_dat <-
   slimmer_PM_dat[, colnames(slimmer_PM_dat) != "trial_noDose"] #remove second trial column
```

@@

```{r DiseasePressure}
slimmer_PM_dat$D_pres <- NA_character_
